[![Build Status](https://travis-ci.org/ivyleavedtoadflax/govstyle.svg?branch=master)](https://travis-ci.org/ivyleavedtoadflax/govstyle)

# govstyle

A package for applying a [gov.uk](http://govuk-elements.herokuapp.com/) style to plots created in the R package [ggplot2](https://github.com/hadley/ggplot2).
This package is in an early stage of development; the intended end point is that it should be fully compliant with the gov.uk style guide.
The best source of docmentation is the vignettes.

## Functions

* `theme_gov()`: Theme to be applied to plots produced in [ggplot2]() to give a government statistics publication feel.
* `gov_cols`: A vector of the [gov.uk](http://govuk-elements.herokuapp.com/colour/#colour-extended-palette) extended palette.
* `check_pal()`: Display the extended gov.uk palette in a pie chart.

## Examples

### theme_gov

```{r, echo=FALSE, include=FALSE}

knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  error = FALSE
  )

```

```{r}

library(ggplot2)
library(dplyr)
#devtools::install_github("ivyleavedtoadflax/govstyle")
library(govstyle)


```

```{r}

p <- mtcars %>%
  ggplot +
  aes(
    x = wt,
    y = mpg,
    col = factor(cyl)
    ) +
  geom_point()

p

p +
  theme_gov()

```

### check_pal

```{r}

## Show gov.uk colours

check_pal()

## Show a subset of gov.uk colours

## Choose n colours:

check_pal(2)

check_pal(3)

check_pal(4)

## Pick a range of colours

check_pal(3:8)

check_pal(c(1,10))

## Pick colours manually

check_pal(
  x = gov_cols[c("green", "grass_green")]
  )

```
